Preliminary Thesis Defence

### 2014-01-06 bitattack.tex
update pictures and bitremit conclusion

The key thing to note here is the perspective of the new cryptocurrency adopt.
Even though the value of Bitcoin is much higher than that of Litecoin, it does not have more to offer.
The lower valued new cryptocurrency is technologically superior and thus more attractive.
Most new cryptocurrencies do not gain momentum and their value is only trivially more than zero.
However, some currencies have gain momentum,
the previously mentioned litecoin introduces a technological innovation and build it base on that.
However, recently a new cryptocurrency has arisen and become quite popular.
This cryptocurrency is called `Dogecoin' and besides it name, it does not introduce any novelty.
Dogecoin is a reference to an internet phenomenon called `Doge Meme'.
Despite the fact that `Dogecoin' does not have a real reason for being considered valuable
(in the sense that cryptocurrencies are considered valuable),
however, by utilising a previously existing internet phenomenon, and it's fan base, this currencies has become valuable.
We thus observe that from the perspective of economic and technological fundamentals,
there is a situation of multiple equilibria.

@@

\begin{figure}
\caption{A Doge Meme}
\label{doge}
%\includegraphics[scale=0.8]{doge.jpg}
\end{figure}

>>>>

The key thing to note here is the perspective of the new cryptocurrency adopt.
Even though the value of Bitcoin is much higher than that of Litecoin, it does not have more to offer.
The lower valued new cryptocurrency is technologically superior and thus more attractive.
Most new cryptocurrencies do not gain momentum and their value is only trivially more than zero.
However, some currencies have gain momentum,
the previously mentioned litecoin introduces a technological innovation and build it base on that.
However, recently a new cryptocurrency has arisen and become quite popular.
This cryptocurrency is called `Dogecoin' and besides it name, it does not introduce any novelty.
Dogecoin is a reference to an internet phenomenon called `Doge Meme'.

Despite the fact that `Dogecoin' does not have a real reason for being considered valuable
(and a name that does not inspire much trust), it has become quite valuable.
This has been done by utilising a previously existing internet phenomenon, and it's existant fan base.
We thus observe that from the perspective of economic and technological fundamentals,
there is a situation of multiple equilibria.

@@

### 2014-01-06 bitremit.tex
update pictures and bitremit conclusion

\section{Data}
\label{btc:data}
Funds held at Bitcoin exchanges are not held in the owners bitcoin wallet.
Rather, the exchange holds them in their wallet, and the clients have a claim on this wallet.
Much like the way bank clients have a claim to their money, which is in the bank's vault.

@@

\begin{itemize}
 \item The blockchain (public ledger)
 \begin{itemize}
 	\item IP address
 	\item Language of transaction notice
 	\item Transaction times
 \end{itemize}
 \item The exchanges
 \begin{itemize}
 	\item Location of exchanges
 	\item Transaction costs for each currency
	\item The order books
	\item Transaction times
 	\item The traded currency
 \end{itemize}
 \item Software
 \begin{itemize}
 	\item Downloads
 	\item Translation contributions (?)
 	\item Connections to server
 \end{itemize}
\end{itemize}

>>>>

\section{Data}
In this section I briefly describe the data which is available to us, in order to undertake such a project.
\label{btc:data}
\begin{itemize}
 \item The blockchain (public ledger)
 \begin{itemize}
 	\item IP address
 	\item Language of transaction notice
 	\item Transaction times
 \end{itemize}
 \item The exchanges
 \begin{itemize}
 	\item Location of exchanges
 	\item Transaction costs for each currency
	\item The order books
	\item Transaction times
 	\item The traded currency
 \end{itemize}
 \item Software
 \begin{itemize}
 	\item Downloads
 	\item Connections to server
 \end{itemize}
\end{itemize}
Funds held at Bitcoin exchanges are not held in the owners bitcoin wallet.
Rather, the exchange holds them in their wallet, and the clients have a claim on this wallet.
Much like the way bank clients have a claim to their money, which is in the bank's vault.

@@

\section{Conclusion}
The Bitcoin transaction mechanism is often mentioned as being interesting for remittances, which are plagued by high costs.
The much more efficient protocol would be a major improvement over established systems.

There are existing networks in many developing (especially African) countries which enable phone to phone transactions.
However, these network (and thus entire economies) are privately owned by telecom providers.
Enableing these phones to conduct Bitcoin transactions would thus have two benefits.
Firstly, the cost of remittances can go down.
Secondly, the economies of phone to phone transactions would no longer be privately owned.

The idea lies thus in linking these two networks, and analysing how the this new mechanism would disseminate itself.
The public nature of the Bitcoin network provides us with a wealth of information which we can use to analyse this dissemination.
